Results

### 2021-07-27 Analysis/03_Summarise_results.Rmd
isolated results per metric

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"))
```
Figure X1: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom).

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"), lm = model_fits, null = null_differences)
```
Figure X2: See above + Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).

@@

# Plots per metric

## Tree metrics

### Alpha

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "tree_alpha", scale.method = "within", level.names = removals, col = cols)
```

### Dispersion

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "tree_dispersion", scale.method = "within", level.names = removals, col = cols)
```

### Evenness

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "tree_evenness", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

## Dissimilarity metrics

### Rao

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "FD_Rao", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Divergence (FD)

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "FD_divergence", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Evenness (FD)

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "FD_evenness", scale.method = "within", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Melodic Rao

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "melodic_Rao", scale.method = "within", level.names = removals, col = cols)
```

### Melodic MPD

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "melodic_mpd", scale.method = "within", level.names = removals, col = cols)
```

## Convex hull metrics

### Convex hull alpha

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "convex.hull", scale.method = "within", level.names = removals, col = cols)
```

## Hypervolume metrics

### Richness

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "hypervolume_richness", scale.method = "within", level.names = removals, col = cols)
```

### Dispersion

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "hypervolume_dispersion", scale.method = "within", level.names = removals, col = cols)
```

### Regularity

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "hypervolume_regularity", scale.method = "within", level.names = removals, col = cols)
```

## Probability density metrics

### Richness

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "TPD_Richness", scale.method = "within", level.names = removals, col = cols)
```

### Evenness

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "TPD_Evenness", scale.method = "within", level.names = removals, col = cols)
```

### Divergence

```{r, fig.height = 4, fig.width = 12}
plot.metric.results(all_results, metric = "TPD_Divergence", scale.method = "within", level.names = removals, col = cols)
```

>>>>

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"))
```

Figure X1: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom).

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"), lm = model_fits, null = null_differences)
```

Figure X2: See above + Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).

@@
